Thermoacoustic heat pumps

### 2023-04-19 paper.tex
first draft of working principles

\section{Working principles}
When a sound wave travels through a tube, gas parcels alternatively compress and expand. This process happens adiabatically. These compressions and expansions change the temperature and pressure of these gas parcels. When the pressure reaches maximum so does the temperature and vice versa. Normally, these temperature differences cancel each other out and the average temperature of the medium stays constant. % FIGURE
A TAHP, however, harnesses these temperature differences in a wave. They do this by using a device called the \emph{stack}. % FIGURE
\newpara{}
The \emph{stack} is designed in such a way that there is a maximum amount of heat transfer from the gas to the stack, but within the stack the heat conduction is limited. The stack should also minimize its obstruction of the gas. A temperature gradient develops on the \emph{stack} when it is placed at a certain location. A heat flow is then generated by placing heat exchangers on both sides of the stack. The reverse of this principle is also true, by applying a temperature gradient to the stack a sound wave can be produced. This system is called a thermoacoustic heat engine or a prime mover, but will not be discussed further in this paper.% FIGURE
\newpara{}
This paper will further discuss the two main types of TAHP, the \emph{standing wave} TAHP and the \emph{traveling wave} TAHP.

\subsection{Standing Waves}
\subsection{Travelling Waves}

>>>>

\section{Working principles}
When a sound wave travels through a tube, gas parcels alternatively compress and expand. This process happens adiabatically. These compressions and expansions change the temperature and pressure of these gas parcels. When the pressure reaches maximum so does the temperature and vice versa. Normally, these temperature differences cancel each other out and the average temperature of the medium stays constant. % FIGURE
A TAHP, however, harnesses these temperature differences in a wave. They do this by using a device called the \emph{stack}. % FIGURE
\newpara{}
The \emph{stack} is designed in such a way that there is a maximum amount of heat transfer from the gas to the stack, but within the stack the heat conduction is limited. The stack should also minimize its obstruction of the gas. A temperature gradient develops on the \emph{stack} when it is placed at a certain location. A heat flow is then generated by placing heat exchangers on both sides of the stack. Minimizing heat conduction in the stack is important to maintain this temperature gradient. The reverse of this principle is also true, by applying a temperature gradient to the stack a sound wave can be produced. This system is called a \emph{thermoacoustic heat engine} or a \emph{prime mover}, but will not be discussed further in this paper.% FIGURE
\newpara{}
This paper will further discuss the two main types of TAHP, the \emph{standing wave} TAHP and the \emph{traveling wave} TAHP.\@
\subsection{Standing Waves}
- COP
- reasonable efficiency and extreme
\subsection{Travelling Waves}
